```{python echo=FALSE}
import python.api_calls as api
import pandas as pd
import warnings

warnings.filterwarnings('ignore')
```
```{r setup, include=FALSE}
#| echo: false
#| warning: false

library(reticulate)
api <- import("python.api_calls")
gain <- api$gain

source("Rscripts/table_formatting.R")

```

# Structure Prioritization {-}


## Field Assessment Ranking Process {-}

A primary outcome of the WCRP will be the rehabilitation of barriers to connectivity in the Horsefly River watershed. To achieve Goal 1 in this plan, it is necessary to identify a suite of barriers that, if rehabilitated, will provide access to a minimum of `r gain` key habitat (@tbl-table16).


```{python echo=FALSE}
#| label: tbl-table16
#| tbl-cap: "Spawning and rearing habitat connectivity gain requirements to meet WCRP goals in the Horsefly River watershed. The measures of currently connected and total habitat values are derived from the Intrinsic Potential habitat model described in Appendix B."
#| warning: false
#| echo: false

# Variables to API calls
connect = api.watershed_connectivity("ALL")[0]
total = round(api.watershed_connectivity("ALL")[1],2) #total km in HORS
access = round(api.watershed_connectivity("ALL")[2],2)
gain = round((total*0.96)-access,2)

# Data frame with table info
df = pd.DataFrame({"Habitat Type":["Spawning and Rearing"],
                   "Currently connected (km)":[str(access)],
                   "Total (km)": [str(total)],
                   "Current Connectivity Status":[str(connect)+"%"],
                   "Goal": ["96%"],
                   "Gain required (km)": [str(gain)]
                   })
                   
# Apply table styling
styled_df = df.style.hide().set_properties(**{'text-align': 'left'})
# header styling
table_styles = [{
       'selector': 'th',
       'props': [('background-color', '#008270'),('text-align', 'left')]
   }]
styled_df.set_table_styles(table_styles)

```

After all existing data and knowledge are collated for known and modelled crossings, an iterative ranking process is conducted to identify barriers for rehabilitation to meet the goals. The ranking process is primarily used to guide field assessments and maximize efficiency in ground truthing data inputs and model outputs, while providing a secondary purpose to evaluate the relative key habitat gains of confirmed barriers in the watershed. This process, combined with input from local knowledge holders and experts, is used to develop field plans for assessing structures that have the potential to block the most key habitat in the watershed.
Field assessments are based on the B.C. [Fish Passage Strategic Approach Environment (2014)](https://www2.gov.bc.ca/assets/gov/environment/plants-animals-and-ecosystems/fish-fish-habitat/fish-passage/strategic20approach20july202014.pdf) and can include a barrier assessment (i.e., evaluating passability of the structure), a habitat confirmation (i.e., evaluation of whether the upstream habitat is suitable for the focal species and whether there are other undocumented man-made or natural barriers upstream or downstream), or a detailed habitat investigation (e.g., a fish passage study or further in-depth analysis of habitat features in a waterbody).

The ranking process accounts for the long-term and immediate  habitat gains potentially offered by each structure to improve key habitat connectivity in the watershed. All structures in the watershed (excluding those confirmed as passable) are ranked in each iteration of the ranking process. Details of the ranking process used to guide field assessments can be found in [Appendix C](data-methods.qmd).

## Structure Prioritization Results {-}

Following field assessments, structures are placed on one of five possible lists: 

1.	Priority barriers list – the structure is confirmed as a full or partial barrier, has key habitat confirmed to exist upstream, and is considered actionable by the planning team (i.e., action items will be identified to advance rehabilitation of the structure). Depending on the barrier, owner, financial constraints, and quality of upstream habitat, the action may be to leave to end of life cycle before reviewing again, remove and decommission the structure, replace with a new passable structure, or modify to temporarily restore connectivity (e.g., fish ladder or baffles installed; (@tbl-priority)).

2.	Assessed structures that remain data deficient list – some form of field assessment has been completed on the structure, but further investigation is required to confirm either the passability status or presence/suitability of upstream habitat (@tbl-deficient).

3.	Rehabilitated barriers list – priority barriers that have been addressed either through removal, replacement, or temporary fish passage improvement projects; (@tbl-rehab).

4.	Non-actionable barriers list – the structure is confirmed to be a barrier to fish passage and have some amount/quality of habitat upstream, but the planning team will not identify actions to advance rehabilitation of the structure because of logistic considerations (e.g., financial costs), short habitat gain, or the upstream habitat is of poor quality or unsuitable in its present condition to support key life stages of the focal species [Appendix C](data-methods.qmd).

5.	Excluded structures list – the structure is excluded from further consideration in subsequent ranking and work planning because the structure is confirmed passable, not present, or there is no key habitat upstream [Appendix C](data-methods.qmd).


```{r priority, echo = FALSE, results = 'asis'}
#| label: tbl-priority
#| tbl-cap: "The Horsefly River watershed priority barrier list, which includes barriers that have undergone field assessment, been reviewed by the planning team, and selected to pursue for proactive rehabilitation."
#| warning: false
#| echo: false

data <- read.csv("data/confirmed_barriers.csv", check.names=FALSE)
prior_num <- nrow(data)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r deficient, echo = FALSE, results = 'asis'}
#| label: tbl-deficient
#| tbl-cap: "Assessed structures that remain data deficient"
#| warning: false
#| echo: false

data <- read.csv("data/assessed_strucDD.csv", check.names=FALSE)
inter_num <- nrow(data)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r rehab, echo = FALSE, results = 'asis'}
#| label: tbl-rehab
#| tbl-cap: "Rehabilitated structures."
#| warning: false
#| echo: false

data <- read.csv("data/rehabilitated_barriers.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```